\documentclass[letterpaper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\input{glyphtounicode}

%----------MARGINS----------
% Kept tight to 0.35in to ensure it fits on one page
\usepackage[margin=0.10in]{geometry}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----------SECTIONS FORMATTING----------
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%----------CUSTOM COMMANDS----------

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingExperience}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% --- BULLET POINT RESTORATION ---
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%
%-------------------------------------------
\begin{document}

%----------HEADING----------
\vspace*{-10pt} 
\begin{center}
    \textbf{\Huge \scshape Sagar Sinha} \\ \vspace{4pt}
    \small (602) 670-3742 $|$
    \href{mailto:sinhasagar507@gmail.com}{sinhasagar507@gmail.com} $|$
    \href{https://linkedin.com/in/sagarsinha2000}{linkedin.com/in/sagarsinha2000} $|$
    \href{https://github.com/sinhasagar507}{github.com/sinhasagar507}
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {MS Computer Science}{Dec 2025}
      {Arizona State University}{\textbf{GPA}: 3.93/4.0}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework}: Data Mining, Applied Regression Analysis, Natural Language Processing, Data Visualization, Distributed Database Systems}
      \resumeItemListEnd
    \resumeSubheading
      {BS Computer Engineering}{May 2022}
      {Pandit Deendayal Energy University}{\textbf{GPA}: 9.02/10.0}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework}: Data Structures, Algorithms, RDBMS, Data Warehousing, Statistics, Machine Learning}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
%-----------TECHNICAL SKILLS----------
% \section{Technical Skills}
% \resumeSubHeadingListStart
%     \item
%       \resumeItemListStart
%         \resumeItem{\textbf{Languages:} Python, SQL (PostgreSQL, MySQL), Go, R, JavaScript, Bash, HTML/CSS}
%         \resumeItem{\textbf{Cloud \& DevOps:} AWS (Lambda, Step Functions, Aurora, S3, Redshift, API Gateway, IAM), Terraform (IaC), Docker, Git, CI/CD, CloudWatch, Linux System Administration}
%         \resumeItem{\textbf{AI \& Machine Learning:} LLMs (Llama, GPT), RAG, Vector Databases (Faiss, LlamaIndex), PyTorch, Hugging Face, Scikit-learn, NLP, Computer Vision (OCR)}
%         \resumeItem{\textbf{Data Engineering:} Apache Spark (PySpark), Airflow, dbt, Snowflake, ETL/ELT Pipelines, Distributed Systems, MongoDB (Sharding), Web Scraping (Selenium, BeautifulSoup)}
%         \resumeItem{\textbf{Analytics \& Tools:} Tableau, Looker Studio, Excel, IBM SPSS, Pandas, NumPy, Statsmodels}
%       \resumeItemListEnd
% \resumeSubHeadingListEnd

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart
    \resumeSubheadingExperience
      {\textbf{AWS Cloud Developer Intern}, Mindsparked}{Mar 2026 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Designed and built event-driven serverless backends} on \textbf{AWS} (Lambda, Step Functions, API Gateway), owning features end-to-end from architectural design through production support and reducing operational overhead by 30\%.}
        \resumeItem{\textbf{Architected scalable data persistence} across \textbf{Aurora PostgreSQL} and \textbf{DynamoDB}, implementing advanced indexing and GSI design that maintained \textbf{99.9\% uptime} and sub-50ms query response times.}
        \resumeItem{\textbf{Automated cloud infrastructure and CI/CD pipelines} using \textbf{Terraform (IaC)}, integrating IAM least-privilege policies and CloudWatch monitoring to enforce auditable, repeatable deployments across environments.}
        \resumeItem{\textbf{Technical Skills: }AWS (Lambda, Aurora, DynamoDB, Step Functions, API Gateway), Terraform, PostgreSQL, Python, CI/CD, Git.}
      \resumeItemListEnd
    \resumeSubheadingExperience
      {\textbf{Software Engineering Externship (AI/ML)}, Extern}{Sep 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Owned end-to-end design and delivery} of a production-ready \textbf{RAG-based OCR engine} in \textbf{Python} for a \textbf{financial-services AI Mortgage Assistant}, automating extraction and indexing of 200+ page documents into a searchable vector store.}
        \resumeItem{\textbf{Optimized a hybrid retrieval system} using \textbf{LlamaIndex}, tuning chunking and embeddings to achieve \textbf{2s median latency} and a Mean Reciprocal Rank (\textbf{MRR}) of \textbf{0.98} across the production prototype.}
        \resumeItem{\textbf{Established operational excellence} for the ML pipeline through real-time logging and system observability, enabling production-grade visibility into document routing, model outputs, and failure modes.}
        \resumeItem{\textbf{Technical Skills: }Python (PyMuPDF, PaddleOCR), Vector Databases (LlamaIndex), NLP, Linux, Observability.}
      \resumeItemListEnd
    \resumeSubheadingExperience
      {\textbf{Data Analyst}, Arizona State University}{Jul 2024 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Architected a cloud-native ELT pipeline} on \textbf{AWS} (\textbf{S3, Redshift}) for 50K+ records, leveraging \textbf{Selenium/BeautifulSoup} scraping of authenticated, JS-rendered sources into a centralized data-persistence layer.}
        \resumeItem{\textbf{Streamlined data integrity through automated testing}, developing unit-test scripts that reduced manual QA intervention by \textbf{60\%} and accelerated reporting cycles for university leadership stakeholders.}
        \resumeItem{\textbf{Transformed wellness data into 40+ actionable KPIs} through automated dashboards, identifying high-risk behavioral trends with \textbf{25\% higher accuracy} than legacy methods.}
        \resumeItem{\textbf{Technical Skills: }Python, AWS (Redshift, S3), SQL, Data Modeling, Cloud Infrastructure, Selenium.}
      \resumeItemListEnd
    \resumeSubheadingExperience
      {\textbf{Data Science Researcher (ML)}, Accredian}{Apr 2023 -- Jul 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Refactored legacy ETL pipelines} for 3,000+ users by migrating monolithic scripts into \textbf{modular Python components}, reducing technical debt by 40\% and improving maintainability of the production environment.}
        \resumeItem{\textbf{Led Root Cause Analysis (RCA) on production bottlenecks}, resolving critical platform issues with a \textbf{90\% success rate} to stabilize system performance during peak traffic.}
        \resumeItem{\textbf{Technical Skills: }Python (PyTorch, NumPy), System Optimization, ML Infrastructure, Production Support.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------RELEVANT PROJECTS-----------
\section{Relevant Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Distributed Banking System}}{}
      \resumeItemListStart
        \resumeItem{Engineered a distributed, \textbf{sharded MongoDB} cluster on \textbf{Docker}, sustaining \textbf{200K+ concurrent requests} with \textbf{sub-70ms read latency} across horizontally partitioned shard nodes.}
        \resumeItem{Implemented automated \textbf{replica-set health checks} and failover monitoring, maintaining \textbf{$>99$\% successful requests} at peak concurrency.}
        \resumeItem{\textbf{Technical Skills:} HTML, CSS, JavaScript, Go, MongoDB, Docker, Bash.}
      \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Socratic CUDA Tutor}}{}
    \resumeItemListStart
        \resumeItem{Won \textbf{2nd Prize and a \$2,000 scholarship} at the \textbf{ASU AI Spark Challenge} for building an AI-powered CUDA tutoring platform with guided conversations, persistent chat history, and module-based learning paths.}
        \resumeItem{Designed interactive learning flows across CUDA fundamentals, memory optimization, and kernel development, backed by a \textbf{RAG pipeline (Faiss)} indexing \textbf{30,000+ CUDA kernels} for context-aware, retrieval-grounded tutoring.}
        \resumeItem{Built an in-browser compile-run-debug workflow with real-time \textbf{GPU performance monitoring}, enabling learners to observe kernel execution and memory utilization with each code iteration.}
        \resumeItem{\textbf{Technical Skills}: React, JavaScript, Flask, Python, Supabase, Ollama, RAG, CUDA, C/C++, Docker, GPU Monitoring.}
    \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Reasoning Capabilities in Discrete Diffusion LLMs}}{}
      \resumeItemListStart
        \resumeItem{Built an \textbf{evaluation harness} for benchmarking \textbf{Discrete Diffusion (Llada-8B) vs. Autoregressive (LlaMA-8B)} models across \textbf{GSM8K and AIME2025} datasets; demonstrated Diffusion SFT superiority on math tasks (\textbf{67\% vs. 56\% accuracy}).}
        \resumeItem{Orchestrated \textbf{repairability experiments} (self-consistency, guided retry), revealing that test-time compute boosts Llada accuracy by \textbf{13.5\%} with zero over-repair compared to AR models.}
        \resumeItem{\textbf{Technical Skills: }Python (Torch), Huggingface, LLM, Supervised Finetuning, Prompting, Evaluation Metrics.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
% \section{Achievements}
% \resumeSubHeadingListStart
%     \resumeSubheadingExperience
%       {\textbf{ASU AI Spark Challenge}}{}
%       \resumeItemListStart
%         \resumeItem{Won 2nd Prize and a \$2,000 scholarship for co-developing \textbf{Socratic AI}, a CUDA programming tutor leveraging Llama 3.2 and a RAG pipeline (Faiss) to index 30,000+ kernels.}
%       \resumeItemListEnd
% \resumeSubHeadingListEnd

\end{document}